Applied Measure Theory for Probabilistic Modeling

### 2022-05-11 paper/paper.tex
edits

The need to preserve this computationally so important locality leads to the new notion of \emph{locally-dominated measure} solving the so-called ``base measure problem'' and making work with densities and distributions in Julia easier and more flexible.

@@

Some sampling algorithms circumvent this problem and only require knowing the density up to a constant factor.

We then can work with the ``unnormalized posterior density'' instead, but we want to distinguish it from a proper probability density, because that difference determines which algorithms are available.

@@

As a second example, people working in Bayesian modeling sometimes use \href{https://en.wikipedia.org/wiki/Prior_probability#Improper_priors}{\emph{improper priors}}. Whatever one's position on the merits of this, we think it's reasonable to make this approach possible. But an improper prior does not integrate to one, so it's not a distribution.
Also, there's an elegant correspondence between frequentist and Bayesian methods, where regularization corresponds to a prior. But limiting ourselves to distributions restrains us from fully realizing this, because the corresponding ``prior'' might be improper or even flat, as in maximum likelihood estimation.

>>>>

The need to preserve this computationally so important locality leads to the new notion of \emph{locally-dominated measure}, solving the so-called ``base measure problem'' and making work with densities and distributions in Julia easier and more flexible.

@@

Some sampling algorithms circumvent this problem and only require knowing the density up to a constant factor.
We then can work with the ``unnormalized posterior density'' instead, but we want to distinguish it from a proper probability density, because that difference determines which algorithms are available.

@@

As a second example, people working in Bayesian modeling sometimes use \href{https://en.wikipedia.org/wiki/Prior_probability#Improper_priors}{\emph{improper priors}}. Whatever one's position on the merits of this, we think it's reasonable to make this approach possible. But an improper prior does not integrate to one, so it's not a distribution.

There's also an elegant correspondence between frequentist and Bayesian methods, where regularization corresponds to a prior. But limiting ourselves to distributions restrains us from fully realizing this, because the corresponding ``prior'' might be improper or even flat, as in maximum likelihood estimation.
